NHF1 Deamination Anchored Excision Site Figure Generation

### 2022-05-20 R/NHF1DeaminationAnchoredExcisionSiteFigureGeneration.rmd
I should have made more intermediate commits
- Added options for filtering (e.g. TGG filtering) as knitting parameters and interactive input.
- Changed mismatch frequency peak calling process to utilize individual positions' z-scores.
- Integrated mismatch frequency z-scores into mismatch frequency plotting.
- Lots of other bugfixes and tweaks. Hopefully the whole project is in a steady-state right now.

---
title: "NHF1 Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
---

@@

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           "deamination_anchored_excision_site_figures"),
                                 .Platform$file.sep))
if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
}

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE
  ))
}
```

```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = "CPD 3' Anchored Nucleotide Frequencies Rep1",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = "CPD 3' Anchored Nucleotide Frequencies Rep2",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = "CPD 5' Anchored Nucleotide Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = "CPD 5' Anchored Nucleotide Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = "CPD 3' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = "CPD 3' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = "CPD 5' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = "CPD 5' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep1",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Nucleotide Frequencies Rep2",
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 5' Anchored Nucleotide Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 5' Anchored Nucleotide Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 3' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 3' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = "6-4 5' Anchored Purine Frequencies Rep1",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = "6-4 5' Anchored Purine Frequencies Rep2",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                         rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
    threePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                        rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
    fivePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}

threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                             rep2 = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR"
    ))
  }
}

fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                            rep2 = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG"
    ))
  }
}
```

```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
                       title = "CPD 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
                       title = "CPD 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
```

```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = "6-4 3' Anchored YR Enrichment Rep1", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = "6-4 3' Anchored YR Enrichment Rep2", secondaryYAxisLabel = "5' Cut Site Distance",
                       showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset,
                       querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = "6-4 5' Anchored TGG Enrichment Rep1", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = "6-4 5' Anchored TGG Enrichment Rep2", secondaryYAxisLabel = "3' Cut Site Distance",
                       showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset, posType = FIVE_PRIME,
                       querySequences = c("TGG"))
```

```{r enrichment_test_1}
for (i in 1:5) {
  testTable = data.table(Read_Length = 9,
                         Read_Sequence = replicate(1000, paste0(sample(c('A','C','G','T'), 9, TRUE), collapse = '')))
  testTableNucFreq = tabulateNucFreqByPosTimepointAndLength(testTable)
  testEnrichment = getSequenceFreqByReadLengthAndPos(testTable, testTableNucFreq, c("CG","CA","TG","TA"))
  plotSequenceEnrichment(testEnrichment, title = "CPD 3' Anchored YR Enrichment Rep1")
}
```

>>>>

---
title: "NHF1 Deamination Anchored Excision Site Figure Generation"
author: "Ben Morledge-Hampton"
date: "5/2/2022"
output: html_document
params:
  bioinformaticsDirectory:
    label: "Bioinformatics Projects Directory"
    value: C:/Bioinformatics_Projects
    input: select
    choices: [C:/Bioinformatics_Projects, F:/Bioinformatics_Projects]
  filtering:
    label: "Filtering"
    value: NONE
    input: select
    choices: [NONE, TGG_filtered]
---

@@

if (interactive()) {
  bioinformaticsDirectory = choose.dir(caption = "Select Bioinformatics_Projects Directory")
  filtering = readline("Filtering identifier (Input nothing for no filtering):")
  if (filtering == '') filtering = character()
} else {
  bioinformaticsDirectory = params$bioinformaticsDirectory
  filtering = params$filtering
  if (filtering == "NONE") filtering = character()
}
if (length(filtering) > 0) {
  titleCaseFiltering = tools::toTitleCase(gsub('_', ' ', filtering))
} else titleCaseFiltering = character()

opts_chunk$set(dev = "png", dpi = 600, fig.width = 7, fig.height = 5, 
               fig.path = paste0(file.path("deamination_analysis_output", cellType,
                                           paste(c(filtering,"deamination_anchored_excision_site_figures"), collapse = '_')),
                                 .Platform$file.sep))

@@

```{r read_nucleotide_frequency_data}
threePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchCPDNucFreq)) {
  threePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(threePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchCPDNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchCPDNucFreq)) {
  fivePrimeMismatchCPDNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMismatchCPDNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}

threePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(threePrimeMismatchSixFourNucFreq)) {
  threePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(threePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "three_prime", anchored = TRUE, filtering = filtering
  ))
}

fivePrimeMismatchSixFourNucFreq = list(rep1 = NULL, rep2 = NULL)
for (i in seq_along(fivePrimeMismatchSixFourNucFreq)) {
  fivePrimeMismatchSixFourNucFreq[[i]] = fread(generateFilePath(
    directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
    cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMismatchSixFourNucFreq)[i],
    strandPolarity = "five_prime", anchored = TRUE, filtering = filtering
  ))
}
```

```{r CPD_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r CPD_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep1, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchCPDNucFreq$rep2, 
                               title = paste(c("CPD", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_nucleotide_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep1"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Nuc Freq Rep2"), collapse = ' '),
                               secondaryYAxisLabel = "5' Cut Site Distance",
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Nuc Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r 6-4_mismatch_anchored_purine_frequencies, fig.width = 11, fig.height = 7}
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(threePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "3' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE, expansionOffset = expansionOffset)

plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep1, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep1"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
plotNucFreqVsReadLengthBarPlot(fivePrimeMismatchSixFourNucFreq$rep2, 
                               title = paste(c("6-4", titleCaseFiltering, "5' Anchored Purine Freq Rep2"), collapse = ' '),
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "3' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE, expansionOffset = expansionOffset)
```

```{r read_sequence_enrichment_data}
threePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                         rep2 = CPDTimepoints)
for (i in seq_along(threePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredCPDEnrichment[[i]])) {
    threePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(threePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredCPDEnrichment = list(rep1 = CPDTimepoints,
                                        rep2 = CPDTimepoints)
for (i in seq_along(fivePrimeMMAnchoredCPDEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredCPDEnrichment[[i]])) {
    fivePrimeMMAnchoredCPDEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "CPD", repitition = names(fivePrimeMMAnchoredCPDEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredCPDEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}

threePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                             rep2 = sixFourTimepoints)
for (i in seq_along(threePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(threePrimeMMAnchoredSixFourEnrichment[[i]])) {
    threePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(threePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(threePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "three_prime",
      anchored = TRUE, sequence = "YR", filtering = filtering
    ))
  }
}

fivePrimeMMAnchoredSixFourEnrichment = list(rep1 = sixFourTimepoints,
                                            rep2 = sixFourTimepoints)
for (i in seq_along(fivePrimeMMAnchoredSixFourEnrichment)) {
  for (j in seq_along(fivePrimeMMAnchoredSixFourEnrichment[[i]])) {
    fivePrimeMMAnchoredSixFourEnrichment[[i]][[j]] = fread(generateFilePath(
      directory = deaminationExcisionSiteDataDirectory, dataTypeStrings$sequenceEnrichment, ".tsv",
      cellType = cellType, lesion = "6-4", repitition = names(fivePrimeMMAnchoredSixFourEnrichment)[i],
      timepoint = names(fivePrimeMMAnchoredSixFourEnrichment[[i]])[j], strandPolarity = "five_prime",
      anchored = TRUE, sequence = "TGG", filtering = filtering
    ))
  }
}
```

```{r CPD_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep1,
                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredCPDEnrichment$rep2,
                       title = paste(c("CPD", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))

plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep1,
                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
plotSequenceEnrichment(fivePrimeMMAnchoredCPDEnrichment$rep2,
                       title = paste(c("CPD", titleCaseFiltering, "5' Anchored TGG Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "3' Cut Site Distance", showThreePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, posType = FIVE_PRIME, querySequences = c("TGG"))
```

```{r 6-4_sequence_enrichment, fig.width = 11, fig.height = 7}
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep1,
                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep1"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
plotSequenceEnrichment(threePrimeMMAnchoredSixFourEnrichment$rep2,
                       title = paste(c("6-4", titleCaseFiltering, "3' Anchored YR Enrichment Rep2"), collapse = ' '),
                       secondaryYAxisLabel = "5' Cut Site Distance", showFivePrimeCutSite = TRUE,
                       expansionOffset = expansionOffset, querySequences = c("CG","CA","TG","TA"))
